Using an iterated block particle filter via \pkg{spatPomp}

### 2022-12-22 ms.Rnw
a few edits

@@

<<model-he10-eval,eval=T,echo=F,fig.height=4, fig.width=6, out.width="6.5in", fig.cap = "Weekly measles case report data for four UK towns.">>=
m_dir <- paste0("m_",i,"/")
if(!dir.exists(m_dir)) dir.create(m_dir)
stew(file=paste0(m_dir,"m-sim.rda"),{
<<model-he10-code>>
})
par(mfrow=c(2,1))
plot(he10_model,log=T)
@

<<he10-sim-plot,echo=F,fig.height=4, fig.width=6, out.width="6.5in", fig.cap = "Simulated data from the \\code{he10} model for four towns">>=
plot(m,log=T)
@

>>>>

\clearpage

@@

<<model-he10-plot,eval=T,echo=F,fig.height=7, fig.width=6, out.width="6.5in", fig.cap = "Weekly measles case reports. (A) Data for four UK towns. (B) Simulated data.">>=
m_dir <- paste0("m_",i,"/")
if(!dir.exists(m_dir)) dir.create(m_dir)
stew(file=paste0(m_dir,"m-sim.rda"),{
<<model-he10-code>>
})
library(grid)
library(cowplot)
plot_data <- plot(he10_model,log=T)+xlab("")
plot_sim <- plot(m,log=T)+xlab("Year")
plot_grid(
  plot_data,
  plot_sim,
  labels=c("A","B"),
  nrow=2,ncol=1
)
@
